---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# educ6600

<!-- badges: start -->
<!-- badges: end -->

The goal of `educ6600` is to provide data and some functions that are useful for the EDUC/PSY 6600 course at Utah State University.

## Installation

You can install the developmental version of educ6600 from GitHub with:

```{r, eval = FALSE}
# install.packages("remotes")  # if remotes not yet installed
remotes::install_github("tysonstanley/educ6600")
```

The data for the examples in the B sections of the homework are found in the package. These can be accessed using the `data()` function. For example, to access the `GRE` data set, we can use:

```{r}
data("GRE")
GRE
```

It contains the following data sets:

- `schizo`
- `GRE`
- `test_scores`
- `memory`
- `data_wait`
- `data_undergrad`
- `data_memory`
- `data_food`
- `child_vars`
- `audience_wide`
- `textbook_wide`
- `memory_wide`
- `tasks_wide`
- `anograms_wide`
- `brain_wide`
- `coupleIQs`
- `speed_voice`
- `data_12b4`
- `schizo_metal`
- `woman_parents`
- `react_wealth`
